\documentclass[margin]{res}
\usepackage{helvetica} % use helvetica.sty
\usepackage{hyperref} % for hyperlinks
\setlength{\textwidth}{5.1in} % set width of text portion

\begin{document}

% Center the name over the entire width of resume:
\moveleft.5\hoffset\centerline{\large\bf PETER JODOGNE}

% Draw a horizontal line the whole width of resume:
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

% address begins here, the address lines must be centered over entire width of resume:
\moveleft.5\hoffset\centerline{386 Hoover Avenue}
\moveleft.5\hoffset\centerline{Bloomfield, NJ 07003}
\moveleft.5\hoffset\centerline{(732) 216-3011}
\moveleft.5\hoffset\centerline{pete.jodogne@gmail.com}

\begin{resume}

\section{OBJECTIVE}
    A position in software engineering with an emphasis on internet technologies, in an environment that encourages advancing one's skills and knowledge.

\section{COMPUTER \\ SKILLS}
    Primary Languages: {\small Javascript, Java} \\
    Hobby Languages: {\small C, Go, Rust} \\
    Frameworks: {\small React, Relay, Redux} \\
    Knowledge: {\small HTML, CSS, SQL, Git, Node.js, Flow, Webpack, Babel, GraphQL}

\section{EXPERIENCE}
    % === 1stdibs =============================================================
    Front End Developer \hfill \textbf{1stdibs, Inc.} \\
    \textsl{February 2015 - current} \hfill Manhattan, NY

    \begin{itemize} \itemsep -2pt %reduce space between items
    \item Developed the build process for the core React component library that the company uses to keep consistent functionality and styling across its sites where single component implementations would have multiple designs which get built and exported as their own components with interchangeable themes. 
    \item Created a scaffolding tool for npm packages that required a transpilation process, helping developers get started on shared packages used by the frontend team without having to mess with webpack, babel, sass, and storybook configurations.
    \item Created the initial frontend implementation for the buyer site's cart feature; the "Call Seller" feature, which in itself involved communication, planning, and integration with a 3rd party service provider; and other high-impact features.
    \end{itemize}

    % === BTX Trader ==========================================================
	Developer \hfill \textbf{BTX Trader} \\
	\textsl{February 2014 - December 2014} \hfill Manhattan, NY

    \begin{itemize} \itemsep -2pt %reduce space between items
    \item Worked as the only developer apart from the CTO in a tiny startup of 4 where I received firsthand experience to the inner workings of developing a product.
    \item Received exposure to the Bitcoin industry and the associated techonologies involved; as well as an understanding of the core concepts of cryptocurrencies i.e. decentralized networks and cryptography.
    \item Helped deliver, design, and implement financial tools and services on the web for the nascent industry.
    \end{itemize}

\section{EDUCATION}
    Bachelor of Science, Computer Science \hfill \textbf{Rutgers State University} \\
    \textsl{Graduated May 2013} \hfill New Brunswick, NJ

    Courses: {\small Internet Technologies, Software Engineering, Operating Systems} \\
    Notable Projects: {\small Multi-threaded bittorrent CLI, Simple FUSE filesystem}

\section{ABOUT ME}
    A curious tinkerer and thinker, indiscriminate of topic. Most of my requested vacation days are spent either traveling, mountain biking or some combination of the two. The majority of my entertainment is from watching sixty symbols videos or David Attenborough nature documentaries. Alright, and maybe Game of Thrones too. \\
    \\
    {\small You can find this resume hosted at github.com/PeteJodo/resume}


\end{resume}
\end{document}
